\makeatletter
\def\section{\@startsection {section}{1}{\z@}{-3.5ex plus -1ex minus 
    -.2ex}{2.3ex plus .2ex}{\center\bf}}
\makeatother
\begin{thebibliography}{99}
\small
\itemsep .5pt plus .2pt minus .1pt
\baselineskip=11.5pt
%
\bibitem{Kato76} T.~Kato, % Tosio Kato
``{\it Perturbation theory for linear operators. Second edition,\/}''
Second edition, % Grundlehren der Mathematischen Wissenschaften, Band 132,
Springer-Verlag, Berlin-New York, 1976.
%
\bibitem{Kobayashi72} S.~Kobayashi, % Shoshichi Kobayash,
Transformation groups in differential geometry,
Ergebnisse der Mathematik und ihrer Grenzgebiete, Band 70,
Springer-Verlag, New York-Heidelberg, 1972.
%
\bibitem{Kobayashi95} S.~Kobayashi, % Shoshichi Kobayash,
Transformation groups in differential geometry,
Reprint of the 1972 edition. Classics in Mathematics,
Springer-Verlag, Berlin, 1995.
%
\bibitem{Lions69} J.-L.~Lions, 
``{\it Quelques m\'ethodes de r\'esolution des probl\`emes aux limites non
lin\'eaires\/},'' Dunod, Gauthier-Villars, Paris 1969.
%
\bibitem{Petersen06} P.~Petersen, % Peter Petersen, 
``{\it Riemannian geometry\/},'' Second edition,
Graduate Texts in Mathematics, 171, Springer, New York, 2006.
%
\bibitem{Shigekawa10} I.~Shigekawa, % Ichiro Shigekawa
Non-symmetric diffusions on a Riemannian manifold,
``{\it Probabilistic approach to geometry\/},'',
Adv.\ Stud.\ Pure Math., 57, pp.~437--461, Math. Soc. Japan, Tokyo, 2010.
%
\bibitem{Stone32} M.~H.~Stone,
Linear transformations in Hilbert space and their applications to analysis,
Amer.\ Math.\ Soc.\ Colloq.\ Publi., {\bf 15}, Providence, 1932.
R. S. Strichartz,
Analysis of Laplacian on the complete Riemannian manifold,
{\it J. Funct. Anal.}, {\bf 52} (1983), 48--79.
%
\bibitem{Tanabe75} 田辺 広城、
発展方程式、岩波書店、東京、1975.
%
\bibitem{YB53} K.~Yano and S.~Bochner,
``{\it Curvature and Betti numbers\/},''
Annals of Mathematics Studies, No. 32,
Princeton University Press, Princeton, N. J., 1953.
%
\end{thebibliography}
